---
title: "Differential gene expression analysis"
date: "`r Sys.Date()`"
output:
  rmdformats::robobook:
    highlight: kate
---

```{r setup, include=FALSE}
library(knitr)
library(rmdformats)
library(DT)

## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=FALSE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

### NOTE

Due to the large size of the table with ~18000 rows, the initial loading of this interactive `HTML` document can take up to **2-3 minutes** or even longer. Please be patient. In case you get a **page unresponsive** message in your browser, choose to **wait** and don’t refresh the page. Refreshing the page will unnecessarily start the page reload from scratch and cause additional delays.


```{r}

#-------------------------------------------------------------------------------
# Interactive DGE tables
#-------------------------------------------------------------------------------

path = "/icgc/dkfzlsdf/analysis/B080/sharma/boulantLab/T84_IL22_IFNL/"
dge  = readRDS(paste0(path, "analysis/DiffExp/diffExpGenes.RDS"))

dge = lapply(dge, function(x){
  x = data.frame(x)
  x[,c(1:3)] = round(x[,c(1:3)], 2)
  x$pvalue = signif(x$pvalue, 2)
  x$padj = signif(x$padj, 2)
  return (x)
})

```

## IL22 24hr vs Mock 24hr

```{r}
datatable(dge$res_24hr_IL22, rownames = TRUE, filter="top", class="compact",
           caption = "Differential gene expression analysis - IL22 24hr",
           extensions = c('Buttons') ,
           options = list(autoWidth = TRUE,
           dom = 'Blfrtip',
           buttons = c('csv', 'excel')))

```
